
\begin{thebibliography}{7}

\bibitem{1}
{Ramadhani, R. A. A., Indriani, F., \& Nugrahadi, D. T. \emph{Comparison of Naive Bayes Smoothing Methods for Twitter Sentiment Analysis. Comparison of Naive Bayes Smoothing Methods for Twitter Sentiment Analysis.}}
\bibitem{2}
{Tsytsarau, M., \& Palpanas, T. (2012). Survey on mining subjective data on the web. \emph{Data Mining and Knowledge Discovery,} 24(3), 478-514}
\bibitem{3}
{Ptáček, T., Habernal, I., \& Hong, J. (2014). Sarcasm detection on czech and english Twitter. In \emph{Proceedings of COLING 2014, the 25th International Conference on Computational Linguistics: Technical Papers} (pp. 213-223).}
\bibitem{4}
{Peng, C. C., Lakis, M., \& Pan, J. W. Detecting Sarcasm in Text.}
\bibitem{5}
{Lunando, E., \& Purwarianti, A. (2013, September). \emph{Indonesian social media sentiment analysis with sarcasm detection.} In \emph{Advanced Computer Science and Information Sistems (ICACSIS), 2013 International Conference on} (pp. 195-198). IEEE.}
\bibitem{6}
{Java, A., Song, X., Finin, T., \& Tseng, B. (2007, August). Why we Twitter: understanding microblogging usage and communities. In \emph{Proceedings of the 9th WebKDD and 1st SNA-KDD 2007 workshop on Web mining and social network analysis}(pp. 56-65). ACM.}

\bibitem{7}
{Karamizadeh, S., Abdullah, S. M., Halimi, M., Shayan, J., \& javad Rajabi, M. (2014, September). Advantage and drawback of \emph{Support Vector Machine} functionality. In \emph{Computer, Communications, and Control Technology (I4CT), 2014 International Conference on} (pp. 63-65). IEEE.}

\bibitem{8}
{Malouf, R. (2002, August). A comparison of algorithms for \emph{Maximum Entropy} parameter estimation. In \emph{proceedings of the 6th conference on Natural language learning-Volume 20 }(pp. 1-7). Association for Computational Linguistics.}

\bibitem{9}
{Chowdhury, G. G. (2003). Natural language processing. \emph{Annual review of information science and technology,} 37(1), 51-89.}

\bibitem{10}
{Liu, B. (2012). Sentiment analysis and opinion mining. \emph{Synthesis lectures on human language technologies, }5(1), 1-167.}

\bibitem{11}
{Baştanlar, Y., \& Özuysal, M. (2014). Introduction to machine learning. \emph{miRNomics: MicroRNA Biology and Computational Analysis,} 105-128.}

\bibitem{12}
{Adriani, M., Asian, J., Nazief, B., Tahaghoghi, S. M., \& Williams, H. E. (2007). Stemming Indonesian: A confix-stripping approach. \emph{ACM Transactions on Asian Language Information Processing (TALIP), }6(4), 1-33.}

\bibitem{13}
{Wicaksono, A. F., \& Purwarianti, A. (2010, August). HMM based part-of-speech tagger for Bahasa Indonesia. In \emph{Fourth International MALINDO Workshop, Jakarta.}}

\bibitem{14}
{Blei, D. M., Ng, A. Y., \& Jordan, M. I. (2003). Latent dirichlet allocation. \emph{Journal of machine Learning research, }3(Jan), 993-1022.}

\bibitem{15}
{Shabtai, A., Moskovitch, R., Elovici, Y., \& Glezer, C. (2009). Detection of malicious code by applying machine learning classifiers on static features: A state-of-the-art survey. \emph{information security technical report,} 14(1), 16-29. }

\bibitem{16}
{Berwick, R. (2003). An Idiot’s guide to Support Vector Machines (SVMs). \emph{Retrieved on October, }21, 2011.}

\bibitem{17}
{Wang, Z., \& Xue, X. (2014). Multi-class \emph{Support Vector Machine}. In \emph{Support Vector Machines Applications }(pp. 23-48). Springer International Publishing.}

\bibitem{18}
{CS 229, Autumn 2009 “The Simplified SMO Algorithm”.}

\bibitem{19}
{Kwak, H., Lee, C., Park, H., \& Moon, S. (2010, April). What is Twitter, a social network or a news media?. In \emph{Proceedings of the 19th international conference on World wide web }(pp. 591-600). ACM.}

\bibitem{20}
{Shamay-Tsoory, S. G., Tomer, R., \& Aharon-Peretz, J. (2005). The neuroanatomical basis of understanding sarcasm and its relationship to social cognition. \emph{Neuropsychology,} 19(3), 288.}
\end{thebibliography}
